---
title: "P8105 Homework 5"
author: "Jesse R. Ames"
date: "11/20/2021"
output: github_document
---

*With assistance from Jeff Goldsmith*

## Problem 1

```{r}
library(tidyverse)
murder <- read_csv("homicide-data.csv", na = c("", "Unknown"))
names(murder)
```

This dataset contains `r nrow(murder)` rows with the following variables:

* `uid` - A unique identifier code
* `reported_date` - Reported date of the homicide
* `victim_last` - Victim's last name
* `victim_first` - Victim's first name
* `victim_race` - Victim's race (White, Black, Hispanic, Asian, or Other)
* `victim_age` - Victim's age (median 28)
* `victim_sex` - Victim's sex (Male, Female)
* `city` and `state`
* `lat` latitude and `lon` longitude
* `disposition` - Status of the case (Closed by arrest, open/no arrest, or closed without arrest)

```{r}
murder <- murder %>%
  #Create city_state variable
  mutate(city_state = str_c(city, state)) %>%
  relocate(city_state) %>%
  #Is the case resolved?
  mutate(resolution = case_when(
    disposition == "Closed by arrest" ~ "solved",
    disposition == "Closed without arrest" ~ "unsolved",
    disposition == "Open/No arrest" ~ "unsolved"
  )) %>%
  filter(city_state != "TulsaAL")
  
#What is the unresolved rate in Baltimore, MD?
baltimore <- murder %>%
  filter(city_state == "BaltimoreMD")
  
balt_sum <- baltimore %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

balt_prop <- prop.test(
  x = balt_sum %>% pull(unsolved),
  n = balt_sum %>% pull(n)
)

balt_prop %>%
  broom::tidy() %>%
  pull(estimate)

#Iterate over all cities
##Create test function
prop_test_function <- function(city_df) {
  city_summary <- city_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test <- prop.test(
    x = city_summary %>% pull(unsolved),
    n = city_summary %>% pull(n)
  )
  
  return(city_test)
}

##Nest and iterate
results <- murder %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))

head(results)

#Plot estimates, CIs
results %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

```{r}
con_exp <- tibble(filepath = paste0("data/", list.files("data")))
con_exp <- con_exp %>%
  #Get arm, subject_id from file names
  mutate(arm = substr(filepath,6,8),
         subject_id = substr(filepath,6,11)) %>%
  
  #Read in data
  mutate(df = map(filepath, read_csv, show_col_types = FALSE)) %>%
  
  #Tidy
  unnest(cols = c(df)) %>%
  pivot_longer(cols = week_1:week_8, names_to = "week", values_to = "measurement") %>%
  mutate(arm = fct_recode(arm, control = "con", experimental = "exp"))
  
#Plot
con_exp %>%
  ggplot(aes(x = week, y = measurement, color = arm, group = subject_id)) +
  geom_line()
```

As the experiment progressed, the experimental group's measurements appear to increase overall relative to the control, though we might want to model this more formally. The appropriate regression model for the marginal trend would be a general linear model (generalized least squares); the appropriate model for the conditional trend would be a linear mixed-effects model.

## Problem 3

```{r}
#library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

#Interpolation function
interpolate <- function(x){
  if (is.numeric(x)) {
    #mean interpolation
    mean_nm <- mean(x, na.rm = TRUE)
    y <- x
    y[which(is.na(y))] <- mean_nm
    return(y)
  }
  else if (is.character(x)) {
    #Fill in with "virginica"
    y <- x
    y[which(is.na(y))] <- "virginica"
    return(y)
  }
}

#map 
iris_with_missing %>%
  map(interpolate)
```